---
title: "Biostat 203B Homework 1"
author: "Fengxue Li"
subtitle: Due Jan 21 @ 11:59PM
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Display machine information for reproducibility:
```{r, eval=F}
sessionInfo()
```

## Q1. Git/GitHub

**No handwritten homework reports are accepted for this course.** We work with Git and GitHub. Efficient and abundant use of Git, e.g., frequent and well-documented commits, is an important criterion for grading your homework.

1. Apply for the [Student Developer Pack](https://education.github.com/pack) at GitHub using your UCLA email. You'll get GitHub Pro account for free (unlimited public and private repositories).

2. Create a **private** repository `biostat-203b-2022-winter` and add `Hua-Zhou` and `maschepps` as your collaborators with write permission.

3. Top directories of the repository should be `hw1`, `hw2`, ... Maintain two branches `main` and `develop`. The `develop` branch will be your main playground, the place where you develop solution (code) to homework problems and write up report. The `main` branch will be your presentation area. Submit your homework files (R markdown file `Rmd`, `html` file converted from R markdown, all code and extra data sets to reproduce results) in `main` branch.

4. After each homework due date, teaching assistant and instructor will check out your main branch for grading. Tag each of your homework submissions with tag names `hw1`, `hw2`, ... Tagging time will be used as your submission time. That means if you tag your `hw1` submission after deadline, penalty points will be deducted for late submission.

5. After this course, you can make this repository public and use it to demonstrate your skill sets on job market.

## Q2. Data ethics training

This exercise (and later in this course) uses the [MIMIC-IV data](https://mimic-iv.mit.edu), a freely accessible critical care database developed by the MIT Lab for Computational Physiology. Follow the instructions at <https://mimic.mit.edu/docs/gettingstarted/> to (1) complete the CITI `Data or Specimens Only Research` course and (2) obtain the PhysioNet credential for using the MIMIC-IV data. Display the verification links to your completion report and completion certificate here. (Hint: The CITI training takes a couple hours and the PhysioNet credentialing takes a couple days; do not leave it to the last minute.)

 **report**
 
 <https://www.citiprogram.org/verify/?k1676b360-e37f-4950-bc0c-b4ddf9a042ce-46526382>
 
**certification**

<https://www.citiprogram.org/verify/?w2a716e01-f093-4bb4-b986-92e71915667b-46526382>



## Q3. Linux Shell Commands

1. The `/mnt/mimiciv/1.0` folder on teaching server contains data sets from MIMIC-IV. Refer to the documentation <https://mimic.mit.edu/docs/iv/> for details of data files.  
    ```{bash}
    pwd
    ls -l /mnt/mimiciv/1.0
    ```
Please, do **not** put these data files into Git; they are big. Do **not** copy them into your directory. Do **not** decompress the gz data files. These create unnecessary big files on storage and are not big data friendly practices. Just read from the data folder `/mnt/mimiciv/1.0` directly in following exercises. 

    Use Bash commands to answer following questions.

2. Display the contents in the folders `core`, `hosp`, `icu`. Why are these data files distributed as `.csv.gz` files instead of `.csv` (comma separated values) files? Read the page <https://mimic.mit.edu/docs/iv/> to understand what's in each folder.

**solution**

```{bash}
# display content of mimiciv data
ls -l /mnt/mimiciv/1.0
# display content of core folder
ls -l /mnt/mimiciv/1.0/core
# display content of icu folder
ls -l /mnt/mimiciv/1.0/icu
# display content of hosp folder
ls -l /mnt/mimiciv/1.0/hosp
```
CSV.GZ is a CSV file compressed. CSV file is very big, so it be compressed to be easier to store and send. Core folder include patient stay information. ICU folder include data collected from cilnical information system used within ICU. HOSP folder include hospital level data form patients, like labs and micro information.

3. Briefly describe what bash commands `zcat`, `zless`, `zmore`, and `zgrep` do.

**solution**

`zcat` command can be used to view the compressed file without uncompressing that file.

`zgrep` command can be used to search inside a compressed file. `zegrep` is like `grep` command in uncompressed file 

`zless` is used to read gz file and paginate it. `zless` is like `less` in uncompressed file 

`zmore` is used to read gz file and paginate it. `zmore` is like `more` in uncompressed file 

4. What's the output of following bash script?
    ```{bash, eval=F}
    for datafile in /mnt/mimiciv/1.0/core/*.gz
      do
        ls -l $datafile
      done
    ```

**solution**

this bash script display all the compressed file in core folder

Display the number of lines in each data file using a similar loop.

```{bash}
for datafile in /mnt/mimiciv/1.0/core/*.gz
  do
   zcat $datafile | wc -l 
  done

```

5. Display the first few lines of `admissions.csv.gz`. How many rows are in this data file? How many unique patients (identified by `subject_id`) are in this data file? (Hint: combine Linux commands `zcat`, `head`/`tail`, `awk`, `sort`, `uniq`, `wc`, and so on.)

**solution**

display the first five lines 
```{bash}
cd /mnt/mimiciv/1.0/core
zcat admissions.csv.gz | head -n 5
```
```{bash}
cd /mnt/mimiciv/1.0/core
zcat admissions.csv.gz | wc -l
```

there are **523741** lines in the file data, including the head

```{bash}
cd /mnt/mimiciv/1.0/core
zcat admissions.csv.gz | awk -F',' '{print $1}' | sort -u |wc -l
```

there are 256879 unique string in the subject_id column (including "subject_id" and patient id), so the there are 256879-1 = **256878** unique patient in the file

6. What are the possible values taken by each of the variable `admission_type`, `admission_location`, `insurance`, and `ethnicity`? Also report the count for each unique value of these variables. (Hint: combine Linux commands `zcat`, `head`/`tail`, `awk`, `uniq -c`, `wc`, and so on.)

**solution**

variable admission_type
```{bash}
cd /mnt/mimiciv/1.0/core
zcat admissions.csv.gz | awk -F',' '{print $6}' | sort |uniq -c
zcat admissions.csv.gz | awk -F',' '{print $6}' | sort -u |wc -l
```

there are **9** admission type in this fata file

variable admission_location

```{bash}
cd /mnt/mimiciv/1.0/core
zcat admissions.csv.gz | awk -F',' '{print $7}' | sort |uniq -c
zcat admissions.csv.gz | awk -F',' '{print $7}' | sort -u |wc -l
```

there are **12** admission location in this data file

variable insurance
```{bash}
cd /mnt/mimiciv/1.0/core
zcat admissions.csv.gz | awk -F',' '{print $9}' | sort |uniq -c
zcat admissions.csv.gz | awk -F',' '{print $9}' | sort -u |wc -l
```
there are **3** admission location in this fata file

variable ethnicity

```{bash}
cd /mnt/mimiciv/1.0/core
zcat admissions.csv.gz | awk -F',' '{print $12}' | sort |uniq -c
zcat admissions.csv.gz | awk -F',' '{print $12}' | sort -u |wc -l
```

there are **8** admission location in this fata file

## Q4. Who's popular in Price and Prejudice

1. You and your friend just have finished reading *Pride and Prejudice* by Jane Austen. Among the four main characters in the book, Elizabeth, Jane, Lydia, and Darcy, your friend thinks that Darcy was the most mentioned. You, however, are certain it was Elizabeth. Obtain the full text of the novel from <http://www.gutenberg.org/cache/epub/42671/pg42671.txt> and save to your local folder. 
    ```{bash, eval=FALSE}
    wget -nc http://www.gutenberg.org/cache/epub/42671/pg42671.txt
    ```
Explain what `wget -nc` does. Do **not** put this text file `pg42671.txt` in Git. Complete the following loop to tabulate the number of times each of the four characters is mentioned using Linux commands.
    ```{bash, eval=FALSE}
    wget -nc http://www.gutenberg.org/cache/epub/42671/pg42671.txt
    for char in Elizabeth Jane Lydia Darcy
    do
      echo $char:
      # some commands here
    done
    ```

**solution**

```{bash}
for char in Elizabeth Jane Lydia Darcy
do
  echo $char:
  grep -o $char pg42671.txt | wc -l
done
```

`wget -nc` means if the file is downloaded more than once in the same directory, the former file will be overwritten.

2. What's the difference between the following two commands?

**solution**
    ```{bash eval=FALSE}
    echo 'hello, world' > test1.txt
    ```
 
means output "hello world" to test1   
    
    ```{bash eval=FALSE}
    echo 'hello, world' >> test2.txt
    ```

means add "hello world" to test2

3. Using your favorite text editor (e.g., `vi`), type the following and save the file as `middle.sh`:
    ```{bash eval=FALSE}
    #!/bin/sh
    # Select lines from the middle of a file.
    # Usage: bash middle.sh filename end_line num_lines
    head -n "$2" "$1" | tail -n "$3"
    ```
Using `chmod` make the file executable by the owner, and run 
    ```{bash eval=FALSE}
    ./middle.sh pg42671.txt 20 5
    ```
Explain the output. Explain the meaning of `"$1"`, `"$2"`, and `"$3"` in this shell script. Why do we need the first line of the shell script?

**solution**

use `chmod` make the file executable by the owner

```{bash}
chmod u+x middle.sh
ls -l
```

```{bash}
./middle.sh pg42671.txt 20 5
```
`"$1"`, `"$2"`, and `"$3"` are the parameters. The output of the command is the 16-20 lines of pg42671.txt file(Pride and Prejudice),the command first select the first 20( parameter `"$2"`)lines of pg42671.txt file (parameter `"$1"`),then the output be piped and select the last 5(parameter `"$3"`) lines from the first output. The final output is the author and edition of the book

The first line of the shell script meaning that the script should always be run with bash

### Q5. More fun with Linux

Try following commands in Bash and interpret the results: `cal`, `cal 2021`, `cal 9 1752` (anything unusual?), `date`, `hostname`, `arch`, `uname -a`, `uptime`, `who am i`, `who`, `w`, `id`, `last | head`, `echo {con,pre}{sent,fer}{s,ed}`, `time sleep 5`, `history | tail`.

**solution**

```{bash}
cal
```
`cal` is today's date showed in calendar
```{bash}
cal 2021
```
`cal 2021` is calendar in 2021

```{bash}
cal 9 1752
```
`cal 9 1752` is calendar in september 1752

```{bash}
date
```
`date` is today's date and time

```{bash}
hostname
```
it shows the hostname of the computer

```{bash}
arch
```

is used to find the computer's architecture type

```{bash}
uname -a
```
this command print kernal name, hostname, kernal release, kernal version, machine hardware name, operating system name

```{bash}
uptime
```
`uptime` shows current time, how long the system is active, number of users currently 
logged into, and the load time for the past 1, 5 and 15 minutes respectively

```{bash}
who am i
```

the username of the computer. because we are not the teaching servers owner, so the command
does show anything. 

```{bash}
who
```
shows users currently logged in to UNIX system

```{bash}
w
```

`w` command shows uptime and show is logged in and what did they do

```{bash}
id
```

`id` command is used to see the user id and group id

```{bash}
last | head
```

`last` command in Linux is used to display the list of all the users logged in and out, `last | head` shows the first few lines of the list

```{bash}
echo {con,pre}{sent,fer}{s,ed}
```

this command gives us the combination of all possible words


```{bash}
time sleep 5
```
```{bash}
history | tail
```

it shows the last few lines of the history. 