---
title: "Biostat 203B Homework 2"
subtitle: Due Feb 6 @ 11:59PM
author: Your Name
output: 
  html_document:
    toc: true
    toc_depth: 4 
---

Display machine information for reproducibility:
```{r}
sessionInfo()
```

```{r setup, message=F}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, cache.lazy = FALSE)
library(tidyverse)
library(data.table)
library(lubridate)
```

```{r}
os <- sessionInfo()$running
if (str_detect(os, "Linux")) {
  mimic_path <- "/mnt/mimiciv/1.0"
} else if (str_detect(os, "macOS")) {
  mimic_path <- "/Users/huazhou/Documents/Box Sync/MIMIC/mimic-iv-1.0"
}
```

In this exercise, we use tidyverse (ggpot2, dplyr, etc) to explore the [MIMIC-IV](https://mimic.mit.edu/docs/iv/) data introduced in [homework 1](https://ucla-biostat-203b.github.io/2022winter/hw/hw1/hw1.html) and to build a cohort of ICU stays.

```{r}
# tree -s -L 2 /Users/huazhou/Documents/Box\ Sync/MIMIC/mimic-iv-1.0
system(str_c("tree -s -L 2 ", shQuote(mimic_path)), intern = TRUE)
```

## Q1. `read.csv` (base R) vs `read_csv` (tidyverse) vs `fread` (data.table)

There are quite a few utilities in R for reading plain text data files. Let us test the speed of reading a moderate sized compressed csv file, `admissions.csv.gz`, by three programs: `read.csv` in base R, `read_csv` in tidyverse, and `fread` in the popular data.table package. 

Which function is fastest? Is there difference in the (default) parsed data types? (Hint: R function `system.time` measures run times.)

For later questions, we stick to the tidyverse.

**solution**

```{r}
#use `read.csv` in base R
system.time(read.csv(str_c(mimic_path, "/core/admissions.csv.gz")))
#use `read_csv` in tidyverse
system.time(read_csv(str_c(mimic_path, "/core/admissions.csv.gz")))
#use `fread` in data.table package
system.time(fread(str_c(mimic_path, "/core/admissions.csv.gz")))
```

`fread` is the fastest 

`read.csv` is data frame , `read_csv` is tibble, `fread` is data.table
 
## Q2. ICU stays

`icustays.csv.gz` (<https://mimic.mit.edu/docs/iv/modules/icu/icustays/>) contains data about Intensive Care Units (ICU) stays. The first 10 lines are
```{r}
system(
  str_c(
    "zcat < ", 
    shQuote(str_c(mimic_path, "/icu/icustays.csv.gz")), 
    " | head"
    ), 
  intern = TRUE
)
```

1. Import `icustatys.csv.gz` as a tibble `icustays_tble`. 

**solution**

```{r}
icustays_tble <- read_csv(str_c(mimic_path, "/icu/icustays.csv.gz"))
```


2. How many unique `subject_id`? Can a `subject_id` have multiple ICU stays? 

**solution**

```{r}
icustays_tble %>% 
  group_by(subject_id) %>% 
  distinct(subject_id) %>% 
  summarise(count = n())
icustays_tble %>% 
  group_by(stay_id) %>% 
  distinct(stay_id) %>% 
  summarise(count = n())
```

there are 53150 unique subject id and 76540 unique ICU time stays. Because the there are more time stays than subject id, so subject id can have multiple time stays.


3. For each `subject_id`, let's only keep the first ICU stay in the tibble `icustays_tble`.

**solution**

```{r}
icustays_tble <- icustays_tble %>% 
  group_by(subject_id) %>% 
  arrange(intime) %>% 
  slice_head(n = 1) %>% 
  print(width = Inf)
```


## Q3. `admission` data

Information of the patients admitted into hospital is available in `admissions.csv.gz`. See <https://mimic.mit.edu/docs/iv/modules/core/admissions/> for details of each field in this file. The first 10 lines are
```{r}
system(
  str_c(
    "zcat < ", 
    shQuote(str_c(mimic_path, "/core/admissions.csv.gz")), 
    " | head"
    ), 
  intern = TRUE
)
```

1. Import `admissions.csv.gz` as a tibble `admissions_tble`.

**solution**

```{r}
admissions_tble <- read_csv(str_c(mimic_path, "/core/admissions.csv.gz"))
```


2. Let's only keep the admissions that have a match in `icustays_tble` according to `subject_id` and `hadmi_id`.

**solution**

```{r}
admissions_tble <- admissions_tble %>%
  semi_join(icustays_tble, by = c("subject_id", "hadm_id")) %>% 
  print(width = Inf)
```


3. Summarize the following variables by graphics. 

**solution**

- admission year 

```{r}
admissions_tble %>%  mutate(admissions_tble,
                     year = year(admissions_tble$admittime)) %>%
  ggplot(mapping = aes(x = year)) +
  geom_bar()
```


- admission month  

```{r}
admissions_tble %>%  mutate(admissions_tble,
                     month = month(admissions_tble$admittime)) %>%
  ggplot(mapping =  aes(x = month)) +
  geom_bar()
```

- admission month day  

```{r}
admissions_tble %>%  mutate(admissions_tble,
                     monthday = mday(admissions_tble$admittime)) %>%
  ggplot(aes(x = monthday)) +
  geom_bar()
```

- admission week day  

```{r}
admissions_tble %>%  mutate(admissions_tble,
                     monthday = wday(admissions_tble$admittime)) %>%
  ggplot(mapping =  aes(x = monthday)) +
  geom_bar()
```

- admission hour (anything unusual?)  

```{r}
admissions_tble %>%  mutate(admissions_tble,
                     hour = hour(admissions_tble$admittime)) %>%
  ggplot(mapping = aes(x = hour)) +
  geom_bar()
```

there are more people in the evening

## Q4. `patients` data

Patient information is available in `patients.csv.gz`. See <https://mimic.mit.edu/docs/iv/modules/core/patients/> for details of each field in this file. The first 10 lines are
```{r}
system(
  str_c(
    "zcat < ", 
    shQuote(str_c(mimic_path, "/core/patients.csv.gz")), 
    " | head"
    ), 
  intern = TRUE
)
```

1. Import `patients.csv.gz` (<https://mimic.mit.edu/docs/iv/modules/core/patients/>) as a tibble `patients_tble` and only keep the patients who have a match in `icustays_tble` (according to `subject_id`).

**solution**

```{r}
patients_tble <- read_csv(str_c(mimic_path,"/core/patients.csv.gz")) %>%
  semi_join(icustays_tble, by = c("subject_id")) %>% 
  print(width = Inf)
```

2. Summarize variables `gender` and `anchor_age`, and explain any patterns you see.

**solution**

```{r}
table(patients_tble$gender)
prop.table(table(patients_tble$gender))
patients_tble %>% ggplot(mapping = aes(x = gender)) +
  geom_bar()
tapply(patients_tble$anchor_age, patients_tble$gender, summary)
```

we can see from the figure and table that men is a little more than women. The anchor age of female is greater than man.

```{r}
summary(patients_tble$anchor_age)
patients_tble %>% ggplot(mapping = aes(x = anchor_age)) +
  geom_bar()
```
most people are from 50-80

## Q5. Lab results

`labevents.csv.gz` (<https://mimic.mit.edu/docs/iv/modules/hosp/labevents/>) contains all laboratory measurements for patients. The first 10 lines are
```{r}
system(
  str_c(
    "zcat < ", 
    shQuote(str_c(mimic_path, "/hosp/labevents.csv.gz")), 
    " | head"
    ), 
  intern = TRUE
)
```
`d_labitems.csv.gz` is the dictionary of lab measurements. 
```{r}
system(
  str_c(
    "zcat < ", 
    shQuote(str_c(mimic_path, "/hosp/d_labitems.csv.gz")), 
    " | head"
    ), 
  intern = TRUE
)
```

1. Find how many rows are in `labevents.csv.gz`.

```{r}
labevents_tble <- 
  read_csv(str_c(mimic_path, "/hosp/labevents_filtered_itemid.csv.gz"),
           col_select = c(subject_id, itemid, charttime, valuenum),
           col_types = cols_only(subject_id = col_double(), 
                                 itemid = col_double(), 
                                 charttime = col_datetime(), 
                                 valuenum = col_double()),
           lazy = TRUE) 
labevents_tble %>% nrow()
```

30198826

2. We are interested in the lab measurements of creatinine (50912), potassium (50971), sodium (50983), chloride (50902), bicarbonate (50882), hematocrit (51221), white blood cell count (51301), glucose (50931), magnesium (50960), and calcium (50893). Retrieve a subset of `labevents.csv.gz` only containing these items for the patients in `icustays_tble` as a tibble `labevents_tble`. 

    Hint: `labevents.csv.gz` is a data file too big to be read in by the `read_csv` function in its default setting. Utilize the `col_select` and `lazy` options in the `read_csv` function to reduce the memory burden.

**solution**

```{r}
itemid <- c(50912, 50971, 50983, 50902, 50882, 51221,
            51301, 50931, 50960, 50893)
labevents_tble <- semi_join(labevents_tble, icustays_tble, 
                             by = c("subject_id")) %>%
  filter(itemid %in% itemid) %>% 
  print(width = Inf)
```


3. Further restrict `labevents_tble` to the first lab measurement during the ICU stay. 

**solution**

```{r}
icu_subset <- icustays_tble %>% 
  select(subject_id, intime)
labevents_tble <- left_join(labevents_tble, icu_subset, 
                            by = c("subject_id")) %>% 
  filter(charttime >= intime) %>% 
  group_by(subject_id, itemid) %>% 
  arrange(charttime) %>% 
  slice_head(n = 1) %>% 
  select(subject_id, itemid, valuenum) %>% 
  ungroup() %>% 
  pivot_wider(names_from = itemid, values_from = valuenum) %>% 
  print(width = Inf)
colnames(labevents_tble) <- c("subject_id", "bicarbonate", "calcium",
                              "chloride", "creatinine", "glucose",
                              "magnesium", "potassium", "sodium",
                              "hematocrit", "white_blood_cell")
```



4. Summarize the lab measurements by appropriate numerics and graphics. 

**soultion**

```{r}
summary(labevents_tble)
labevents_tble %>% 
  ggplot(mapping = aes(x = bicarbonate)) +
  geom_histogram(outlier.shape = NA) 
labevents_tble %>% 
  ggplot(mapping = aes(x = calcium)) +
  geom_histogram(outlier.shape = NA) +
  xlim(0, 15)
labevents_tble %>% 
  ggplot(mapping = aes(x = chloride)) +
  geom_histogram(outlier.shape = NA) +
  xlim(50, 130)
labevents_tble %>% 
  ggplot(mapping = aes(x = creatinine)) +
  geom_histogram(outlier.shape = NA) +
  xlim(-5, 15)
labevents_tble %>% 
  ggplot(mapping = aes(x = glucose)) +
  geom_histogram(outlier.shape = NA) +
  xlim(-20, 600)
labevents_tble %>% 
  ggplot(mapping = aes(x = magnesium)) +
  geom_histogram(outlier.shape = NA) +
  xlim(0, 8)
labevents_tble %>% 
  ggplot(mapping = aes(x = potassium)) +
  geom_histogram(outlier.shape = NA) +
  xlim(2, 10)
labevents_tble %>% 
  ggplot(mapping = aes(x = sodium)) +
  geom_histogram(outlier.shape = NA) +
  xlim(100, 170)
labevents_tble %>% 
  ggplot(mapping = aes(x = hematocrit)) +
  geom_histogram(outlier.shape = NA)
labevents_tble %>% 
  ggplot(mapping = aes(x = white_blood_cell)) +
  geom_histogram(outlier.shape = NA) +
  xlim(-5, 70)

```



## Q6. Vitals from charted events

`chartevents.csv.gz` (<https://mimic.mit.edu/docs/iv/modules/icu/chartevents/>) contains all the charted data available for a patient. During their ICU stay, the primary repository of a patient’s information is their electronic chart. The `itemid` variable indicates a single measurement type in the database. The `value` variable is the value measured for `itemid`. The first 10 lines of `chartevents.csv.gz` are
```{r}
system(
  str_c(
    "zcat < ", 
    shQuote(str_c(mimic_path, "/icu/chartevents.csv.gz")), 
    " | head"), 
  intern = TRUE
)
```
`d_items.csv.gz` (<https://mimic.mit.edu/docs/iv/modules/icu/d_items/>) is the dictionary for the `itemid` in `chartevents.csv.gz`. 
```{r}
system(
  str_c(
    "zcat < ", 
    shQuote(str_c(mimic_path, "/icu/d_items.csv.gz")), 
    " | head"), 
  intern = TRUE
)
```

1. We are interested in the vitals for ICU patients: heart rate (220045), mean non-invasive blood pressure (220181), systolic non-invasive blood pressure (220179), body temperature in Fahrenheit (223761), and respiratory rate (220210). Retrieve a subset of `chartevents.csv.gz` only containing these items for the patients in `icustays_tble` as a tibble `chartevents_tble`.

**solution**

```{r}
chartevents_tble <- 
  read_csv(str_c(mimic_path, "/icu/chartevents_filtered_itemid.csv.gz"),
           col_select = c(subject_id, itemid, charttime, valuenum),
           col_types = cols_only(subject_id = col_double(), 
                                 itemid = col_double(), 
                                 charttime = col_datetime(), 
                                 valuenum = col_double()),
           lazy = TRUE)
```

```{r}
itemid <- c(220045, 220181, 220179, 223761, 220210)
chartevents_tble <- semi_join(chartevents_tble,icustays_tble, 
                             by = c("subject_id")) %>%
  filter(itemid %in% itemid) %>% 
  print(width = Inf)
```


2. Further restrict `chartevents_tble` to the first vital measurement during the ICU stay. 

**solution**

```{r}
icu_subset <- icustays_tble %>% 
  select(subject_id, intime)
chartevents_tble <- left_join(chartevents_tble, icu_subset, 
                            by = c("subject_id")) %>% 
  filter(charttime >= intime) %>% 
  group_by(subject_id, itemid) %>% 
  arrange(charttime) %>% 
  slice_head(n = 1) %>% 
  select(subject_id, itemid, valuenum) %>% 
  ungroup() %>% 
  pivot_wider(names_from = itemid, values_from = valuenum) %>% 
  print(width = Inf) 
colnames(chartevents_tble) <- c("subject_id", "heart_rate", 
                                "systolic_blood_pressure",
                                "mean_blood_pressure",
                                "respiratory_rate",
                                "body_temperature")
```

53150

3. Summarize these vital measurements by appropriate numerics and graphics. 

**solution**

```{r}
summary(chartevents_tble)
chartevents_tble %>% 
  ggplot(mapping = aes(x = heart_rate)) +
  geom_histogram(outlier.shape = NA) +
  xlim(-5, 200)
chartevents_tble %>% 
  ggplot(mapping = aes(x = systolic_blood_pressure)) +
  geom_histogram(outlier.shape = NA) +
  xlim(-5, 220)
chartevents_tble %>% 
  ggplot(mapping = aes(x = mean_blood_pressure)) +
  geom_histogram(outlier.shape = NA) +
  xlim(-5, 200)
chartevents_tble %>% 
  ggplot(mapping = aes(x = respiratory_rate)) +
  geom_histogram(outlier.shape = NA) +
  xlim(-5, 60)
chartevents_tble %>% 
  ggplot(mapping = aes(x = body_temperature)) +
  geom_histogram(outlier.shape = NA) +
  xlim(90, 105)
```

## Q7. Putting things together

Let us create a tibble `mimic_icu_cohort` for all ICU stays, where rows are  

- first ICU stay of each unique adult (age at admission > 18)

and columns contain at least following variables  

- all variables in `icustays.csv.gz`  
- all variables in `admission.csv.gz`  
- all variables in `patients.csv.gz`  
- first lab measurements during ICU stay  
- first vital measurements during ICU stay
- an indicator variable `thirty_day_mort` whether the patient died within 30 days of hospital admission (30 day mortality)

**solution**

```{r}
mimic_icu_cohort <- 
  left_join(icustays_tble, admissions_tble, by = "subject_id") %>%
  left_join(patients_tble, by = "subject_id") %>% 
  left_join(labevents_tble, by = "subject_id") %>% 
  left_join(chartevents_tble, by = "subject_id") %>% 
  mutate(age = anchor_age + year(admittime) - anchor_year) %>% 
  filter(age > 18) %>% 
  mutate(thirty_day_mort = "No") %>% 
  mutate(minus = (deathtime - admittime))  
mimic_icu_cohort$thirty_day_mort <- 
  ifelse(is.na(mimic_icu_cohort$deathtime), "No",
  ifelse(mimic_icu_cohort$deathtime - mimic_icu_cohort$admittime <= 2592000,
                                            "Yes", "No"))
```



## Q8. Exploratory data analysis (EDA)

Summarize following information using appropriate numerics or graphs.

**solution**

- `thirty_day_mort` vs demographic variables (ethnicity, language, insurance, marital_status, gender, age at hospital admission)

**ethnicity**

```{r}
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "Yes") %>% 
  group_by(ethnicity) %>% 
  ggplot(mapping = aes(x = "", fill = ethnicity)) + 
  geom_bar(width = 1) + 
  coord_polar("y") +
  labs(title = "Patient died within 30 days of hospital admission")
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "No") %>% 
  group_by(ethnicity) %>% 
  ggplot(mapping = aes(x = "", fill = ethnicity)) + 
  geom_bar(width = 1) + 
  coord_polar("y") +
  labs(title = "Patient did not die within 30 days of hospital admission")
```

For ethnicity, the proportion of white people are more which did not die in the hospital  compared to people died in the hospital within 30 days. The proportion of unknown ethnicity and black/aferican american people are greater for people died in hospital within 30 days.

**language**
```{r}
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "Yes") %>% 
  group_by(language) %>% 
  ggplot(mapping = aes(x = "", fill = language)) + 
  geom_bar(width = 1) + 
  coord_polar("y") +
  labs(title = "Patient died within 30 days of hospital admission")
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "No") %>% 
  group_by(language) %>% 
  ggplot(mapping = aes(x = "", fill = language)) + 
  geom_bar(width = 1) + 
  coord_polar("y") +
  labs(title = "Patient did not die within 30 days of hospital admission")
```

The proportion of using English are almost same for people died in hospital within 30 days and who are not

**insurance**
```{r}
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "Yes") %>% 
  group_by(insurance) %>% 
  ggplot(mapping = aes(x = "", fill = insurance)) + 
  geom_bar(width = 1) + 
  coord_polar("y") +
  labs(title = "Patient died within 30 days of hospital admission")
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "No") %>% 
  group_by(insurance) %>% 
  ggplot(mapping = aes(x = "", fill = insurance)) + 
  geom_bar(width = 1) + 
  coord_polar("y") +
  labs(title = "Patient did not die within 30 days of hospital admission")
```

The proportion of medicare are more and medicaid are less for people died in hospital within 30 days and who are not.

**marital_status**

```{r}
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "Yes") %>% 
  group_by(marital_status) %>% 
  ggplot(mapping = aes(x = "", fill = marital_status)) + 
  geom_bar(width = 1) + 
  coord_polar("y") +
  labs(title = "Patient died within 30 days of hospital admission")
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "No") %>% 
  group_by(marital_status) %>% 
  ggplot(mapping = aes(x = "", fill = marital_status)) + 
  geom_bar(width = 1) + 
  coord_polar("y") +
  labs(title = "Patient did not die within 30 days of hospital admission")
```

The proportion of single and married are less for people died in hospital within 30 days and who are not. But The proportion of widowed are more for people died in hospital within 30 days and who are not

**gender**

```{r}
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "Yes") %>% 
  group_by(gender) %>% 
  ggplot(mapping = aes(x = "", fill = gender)) + 
  geom_bar(width = 1) + 
  coord_polar("y") +
   labs(title = "Patient died within 30 days of hospital admission")
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "No") %>% 
  group_by(gender) %>% 
  ggplot(mapping = aes(x = "", fill = gender)) + 
  geom_bar(width = 1) + 
  coord_polar("y") +
  labs(title = "Patient did not die within 30 days of hospital admission")
```

The proportion of female are more for people died in hospital within 30 days and who are not

**age at hospital admission**
```{r}
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "Yes") %>% 
  ggplot(mapping = aes(x = age)) +
  geom_histogram(outlier.shape = NA) +
  labs(title = "Patient died within 30 days of hospital admission")
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "No") %>% 
  ggplot(mapping = aes(x = age)) +
  geom_histogram(outlier.shape = NA) +
  labs(title = "Patient did not die within 30 days of hospital admission")
tapply(mimic_icu_cohort$age, mimic_icu_cohort$thirty_day_mort, summary)
```

for people who did not died in hospital with in 30 days, their age centered at 55-80, but for people who died in 30 days, many of them are older 80. And we can see that the median and mean are greater for people died in the hospital.


- `thirty_day_mort` vs first lab measurements

```{r}
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "Yes") %>% 
  select(bicarbonate, calcium, chloride, creatinine, glucose, magnesium, 
         potassium, sodium, hematocrit, white_blood_cell) %>%
  summary()
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "No") %>% 
  select(bicarbonate, calcium, chloride, creatinine, glucose, magnesium, 
         potassium, sodium, hematocrit, white_blood_cell) %>%
  summary()
```



- `thirty_day_mort` vs first vital measurements

```{r}
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "Yes") %>% 
  select(bicarbonate, systolic_blood_pressure, mean_blood_pressure, 
         body_temperature, respiratory_rate) %>%
  summary()
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "No") %>% 
  select(bicarbonate, systolic_blood_pressure, mean_blood_pressure, 
         body_temperature, respiratory_rate) %>%
  summary()
```


- `thirty_day_mort` vs first ICU unit

**first ICU type in which the patient was cared for**

```{r}
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "Yes") %>% 
  group_by(first_careunit) %>% 
  ggplot(mapping = aes(x = "", fill = first_careunit)) + 
  geom_bar(width = 1) + 
  coord_polar("y") +
  labs(title = "Patient died within 30 days of hospital admission")
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "No") %>% 
  group_by(first_careunit) %>% 
  ggplot(mapping = aes(x = "", fill = first_careunit)) + 
  geom_bar(width = 1) + 
  coord_polar("y") +
  labs(title = "Patient did not die within 30 days of hospital admission")
```

**last ICU type in which the patient was cared for**

```{r}
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "Yes") %>% 
  group_by(last_careunit) %>% 
  ggplot(mapping = aes(x = "", fill = last_careunit)) + 
  geom_bar(width = 1) + 
  coord_polar("y") +
  labs(title = "Patient died within 30 days of hospital admission")
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "No") %>% 
  group_by(last_careunit) %>% 
  ggplot(mapping = aes(x = "", fill = last_careunit)) + 
  geom_bar(width = 1) + 
  coord_polar("y") +
  labs(title = "Patient did not die within 30 days of hospital admission")
```

**length of stay for the patient for the given ICU stay**

```{r}
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "Yes") %>% 
  ggplot(mapping = aes(x = los)) +
  geom_histogram(outlier.shape = NA) +
  xlim(0, 40) + 
  labs(title = "Patient died within 30 days of hospital admission") 
mimic_icu_cohort %>% 
  filter(thirty_day_mort == "No") %>% 
  ggplot(mapping = aes(x = los)) +
  geom_histogram(outlier.shape = NA) +
  labs(title = "Patient did not die within 30 days of hospital admission") +
  xlim(0, 40)
tapply(mimic_icu_cohort$los, mimic_icu_cohort$thirty_day_mort, summary)
```







